%----------------------------------------------------------------------------------------
%  DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%  FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%  PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip}

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X}

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by:
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}
\newcommand{
  \itemmarker}{{\small\textbullet}}
%----------------------------------------------------------------------------------------
%  BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
  \pagestyle{empty}

%----------------------------------------------------------------------------------------
%  TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

  \begin{tabularx}{\linewidth}{@{} C @{}}
    \Huge{\textbf{Bari Vakhidov}} \\[7.5pt]
    \href{https://github.com/BariVakhidov}{\raisebox{-0.05\height}\faGithub\ BariVakhidov} \ $|$ \
    \href{https://linkedin.com/in/bariVahidov}{\raisebox{-0.05\height}\faLinkedin\ bariVakhidov} \ $|$ \
    \href{https://t.me/Meme_hunt}{\raisebox{-0.05\height}\faTelegram\ BariVakhidov} \ $|$ \
    \href{mailto:vahidovbari@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ vahidovbari@gmail.com} \
  \end{tabularx}

%----------------------------------------------------------------------------------------
%  SKILLS
%----------------------------------------------------------------------------------------
  \section{Skills}\label{sec:skills}
  \begin{tabularx}{\linewidth}{@{}l X@{}}
    \itemmarker & \normalsize{Go $|$ TypeScript $|$ JavaScript $|$ Java $|$  Node.js $|$ Express.js $|$ React }\\
    \itemmarker & \normalsize{PostgreSQL $|$ Kafka $|$ Redis $|$ MongoDB $|$ go-chi $|$ pgx $|$ sqlc $|$ mockery $|$ Prometheus $|$ Grafana}\\
    \itemmarker & \normalsize{REST $|$ gRPC $|$ Websocket $|$ CI/CD $|$ Docker $|$ Git $|$ Swagger $|$ Elasticsearch $|$ Kibana $|$ Alertmanager}\\
  \end{tabularx}

%Experience
  \section{Experience}\label{sec:experience}

  \begin{tabularx}{\linewidth}{ @{}l r@{} }
    \textbf{Senior Full-stack developer $|$ \underline{The Open Platform, Tribute}} & \hfill remote, \textbf{Nov 2024 - now} \\[3.75pt]
    \multicolumn{2}{@{}X@{}}{
      \begin{minipage}[t]{\linewidth}
        \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
          \item[--] Built a multi-currency exchange mechanism with an integrated currency rates provider for a Telegram content monetization service, \textbf{increasing project margin by 7\%}.
          \item[--] Implemented a trial subscription and a notification system for unpaid subscriptions, improving user acquisition and payment compliance. Refactored payment systems and enhanced the 3DS flow for a more reliable payment experience. Implemented unit and functional tests.
          \item[--] Managed a 7-person full-stack team, driving development, reviews, releases, and recruitment.
Boosted frontend efficiency, \textbf{cutting load times by 35\%}, improving UX and retention.
        \end{itemize}
      \end{minipage}
    }
  \end{tabularx}

  \begin{tabularx}{\linewidth}{ @{}l r@{} }
    \textbf{Senior Full-stack developer $|$ \underline{Invitro IT}} & \hfill remote, \textbf{Feb 2022 - Sep 2024} \\[3.75pt]
    \multicolumn{2}{@{}X@{}}{
      \begin{minipage}[t]{\linewidth}
        \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
          \item[--] Designed and implemented internal microservices and frontend applications for the largest medical company in the Commonwealth of Independent States, with \textbf{a daily turnover exceeding \$2 million}, using Go, TypeScript.
          \item[--] Developed an internal gRPC authentication service utilizing JWT tokens.
          \item[--] Rewrote several microservices to transition a legacy project based on Java 8 and Spring Boot to Go.
          \item[--] Established an API gateway in Go for the company's main internal project, simplifying integration with other services and clients.
          \item[--] Configured bundlers and optimized the application's code, resulting in \textbf{an 80\% improvement in performance and reduced load times}.
          \item[--] Integrated monitoring and error tracking services (Sentry.IO, Elasticsearch, Prometheus, Alertmanager, Grafana) for internal applications. Added unit tests and end-to-end tests.
          \item[--] Integrated Continuous Integration/Deployment pipelines using Docker and Kubernetes.
          \item[--] Led a frontend team of 5 members on internal products, mentored junior developers, and assisted teammates in enhancing their skills; handled merge requests and code reviews, and actively participated in the hiring process.
        \end{itemize}
      \end{minipage}
    }
  \end{tabularx}

  \begin{tabularx}{\linewidth}{ @{}l r@{} }
    \textbf{Senior Frontend developer $|$ \underline{Noveo Group}} & \hfill Cyprus, Limassol, remote, \textbf{Oct 2021 - Dec 2022}\\[3.75pt]
    \multicolumn{2}{@{}X@{}}{
      \begin{minipage}[t]{\linewidth}
        \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
          \item[--] Contributed to the outsourced development of commercial projects, involved in both the creation from scratch and integration with legacy projects.
          \item[--] Designed and developed chat and planning modules and B2B application for social activities.
          \item[--] Collaborated closely with Node.js developers to ensure the development of well-designed products.
          \item[--] Managed team members, actively participated in scrum activities, provided consultation to colleagues, and evaluated risks.
        \end{itemize}
      \end{minipage}
    }
  \end{tabularx}

%----------------------------------------------------------------------------------------
%  EDUCATION
%----------------------------------------------------------------------------------------
  \section{Education}\label{sec:education}
  \begin{tabularx}{\linewidth}{@{}l X@{}}
    2016--2020 & Bachelor of Engineering at \textbf{Saint Petersburg Mining University} \hfill \normalsize (GPA: 4.7/5.0) \\
    2013--2016 & Mathematics Degree at \textbf{AG SPSU — Academic Gymnasium} \hfill (GPA: 4.8/5.0) \\
  \end{tabularx}

  \vfill
\end{document}
